Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-05-21 affiliations.tex
Updates from Overleaf

$^{8}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
$^{9}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{10}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{11}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
$^{12}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{13}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{14}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{15}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{16}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{17}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
$^{18}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\

>>>>

$^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
$^{11}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{13}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{14}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{15}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
$^{16}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
$^{17}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{18}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\

### 2021-05-21 draft.tex
Updates from Overleaf

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Sullivan,$^{1}$
M.~Smith,$^{2,1}$
C.~Frohmaier,$^{1,3}$
M.~Vincenzi,$^{3}$
O.~Graur,$^{3}$
B.~Popovic,$^{4}$
P.~Armstrong,$^{5}$
D.~Brout,$^{6,7}$
D.~Carollo,$^{8}$
T.~M.~Davis,$^{9}$
L.~Galbany,$^{10}$
S.~R.~Hinton,$^{9}$
L.~Kelsey,$^{1}$
R.~Kessler,$^{11,12}$
G.~F.~Lewis,$^{13}$
C.~Lidman,$^{14,5}$
A.~M\"oller,$^{15}$
R.~C.~Nichol,$^{3}$
B.~Rose,$^{4}$
D.~Scolnic,$^{4}$
M.~Toy,$^{1}$
B.~E.~Tucker,$^{5}$
Z.~Zontou,$^{1}$
J.~Asorey,$^{16}$
T.~M.~C.~Abbott,$^{17}$
M.~Aguena,$^{18,19}$
S.~Allam,$^{20}$
F.~Andrade-Oliveira,$^{21,19}$
J.~Annis,$^{20}$
D.~Bacon,$^{3}$
E.~Bertin,$^{22,23}$
D.~Brooks,$^{24}$
E.~Buckley-Geer,$^{11,20}$
D.~L.~Burke,$^{25,26}$
A.~Carnero~Rosell,$^{27,19,28}$
M.~Carrasco~Kind,$^{29,30}$
J.~Carretero,$^{31}$
M.~Costanzi,$^{32,33,34}$
L.~N.~da Costa,$^{19,35}$
M.~E.~S.~Pereira,$^{36}$
S.~Desai,$^{37}$
H.~T.~Diehl,$^{20}$
P.~Doel,$^{24}$
S.~Everett,$^{38}$
I.~Ferrero,$^{39}$
B.~Flaugher,$^{20}$
P.~Fosalba,$^{40,41}$
J.~Frieman,$^{20,12}$
J.~Garc\'ia-Bellido,$^{42}$
E.~Gaztanaga,$^{40,41}$
T.~Giannantonio,$^{43,44}$
D.~Gruen,$^{45,25,26}$
R.~A.~Gruendl,$^{29,30}$
J.~Gschwend,$^{19,35}$
G.~Gutierrez,$^{20}$
D.~L.~Hollowood,$^{38}$
K.~Honscheid,$^{46,47}$
B.~Hoyle,$^{48,49}$
D.~J.~James,$^{7}$
E.~Krause,$^{50}$
K.~Kuehn,$^{51,52}$
N.~Kuropatkin,$^{20}$
M.~A.~G.~Maia,$^{19,35}$
J.~L.~Marshall,$^{53}$
P.~Martini,$^{46,54,55}$
F.~Menanteau,$^{29,30}$
R.~Miquel,$^{56,31}$
R.~Morgan,$^{57}$
R.~L.~C.~Ogando,$^{19,35}$
A.~Palmese,$^{20,12}$
F.~Paz-Chinch\'{o}n,$^{29,43}$
D.~Petravick,$^{29}$
A.~Pieres,$^{19,35}$
A.~A.~Plazas~Malag\'on,$^{58}$
A.~K.~Romer,$^{59}$
E.~Sanchez,$^{16}$
V.~Scarpine,$^{20}$
M.~Schubnell,$^{36}$
S.~Serrano,$^{40,41}$
I.~Sevilla-Noarbe,$^{16}$
E.~Suchyta,$^{60}$
M.~E.~C.~Swanson,$^{29}$
G.~Tarle,$^{36}$
D.~Thomas,$^{3}$
C.~To,$^{45,25,26}$
T.~N.~Varga,$^{49,61}$
and A.~R.~Walker$^{17}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

>>>>

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\usepackage{eso-pic}% http://ctan.org/pkg/eso-pic

\AddToShipoutPictureBG*{%
  \AtPageUpperLeft{%
    \hspace{0.75\paperwidth}%
    \raisebox{-4.5\baselineskip}{%
      \makebox[0pt][l]{\textnormal{DES-2021-0642}}
}}}%

\AddToShipoutPictureBG*{%
  \AtPageUpperLeft{%
    \hspace{0.75\paperwidth}%
    \raisebox{-5.5\baselineskip}{%
      \makebox[0pt][l]{\textnormal{FERMILAB-PUB-21-245-AE}}
}}}%

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Sullivan,$^{1}$
M.~Smith,$^{2,1}$
C.~Frohmaier,$^{3,1}$
M.~Vincenzi,$^{3}$
O.~Graur,$^{3}$
B.~Popovic,$^{4}$
P.~Armstrong,$^{5}$
D.~Brout,$^{6,7}$
T.~M.~Davis,$^{8}$
L.~Galbany,$^{9}$
S.~R.~Hinton,$^{8}$
L.~Kelsey,$^{1}$
R.~Kessler,$^{10,11}$
C.~Lidman,$^{12,5}$
A.~M\"oller,$^{13}$
R.~C.~Nichol,$^{3}$
B.~Rose,$^{4}$
D.~Scolnic,$^{4}$
M.~Toy,$^{1}$
Z.~Zontou,$^{1}$
J.~Asorey,$^{14}$
D.~Carollo,$^{15}$
K.~Glazebrook,$^{16}$
G.~F.~Lewis,$^{17}$
B.~E.~Tucker,$^{5}$
T.~M.~C.~Abbott,$^{18}$
M.~Aguena,$^{19}$
S.~Allam,$^{20}$
F.~Andrade-Oliveira,$^{21,19}$
J.~Annis,$^{20}$
D.~Bacon,$^{3}$
E.~Bertin,$^{22,23}$
D.~Brooks,$^{24}$
E.~Buckley-Geer,$^{10,20}$
D.~L.~Burke,$^{25,26}$
A.~Carnero~Rosell,$^{27,19,28}$
M.~Carrasco~Kind,$^{29,30}$
J.~Carretero,$^{31}$
M.~Costanzi,$^{32,33,34}$
L.~N.~da Costa,$^{19,35}$
M.~E.~S.~Pereira,$^{36}$
S.~Desai,$^{37}$
H.~T.~Diehl,$^{20}$
P.~Doel,$^{24}$
S.~Everett,$^{38}$
I.~Ferrero,$^{39}$
B.~Flaugher,$^{20}$
P.~Fosalba,$^{40,41}$
J.~Frieman,$^{20,11}$
J.~Garc\'ia-Bellido,$^{42}$
E.~Gaztanaga,$^{40,41}$
T.~Giannantonio,$^{43,44}$
D.~Gruen,$^{45,25,26}$
R.~A.~Gruendl,$^{29,30}$
J.~Gschwend,$^{19,35}$
G.~Gutierrez,$^{20}$
D.~L.~Hollowood,$^{38}$
K.~Honscheid,$^{46,47}$
B.~Hoyle,$^{48,49}$
D.~J.~James,$^{7}$
E.~Krause,$^{50}$
K.~Kuehn,$^{51,52}$
N.~Kuropatkin,$^{20}$
M.~A.~G.~Maia,$^{19,35}$
J.~L.~Marshall,$^{53}$
P.~Martini,$^{46,54,55}$
F.~Menanteau,$^{29,30}$
R.~Miquel,$^{56,31}$
R.~Morgan,$^{57}$
R.~L.~C.~Ogando,$^{19,35}$
A.~Palmese,$^{20,11}$
F.~Paz-Chinch\'{o}n,$^{29,43}$
D.~Petravick,$^{29}$
A.~Pieres,$^{19,35}$
A.~A.~Plazas~Malag\'on,$^{58}$
A.~K.~Romer,$^{59}$
E.~Sanchez,$^{14}$
V.~Scarpine,$^{20}$
M.~Schubnell,$^{36}$
S.~Serrano,$^{40,41}$
I.~Sevilla-Noarbe,$^{14}$
M.~Soares-Santos,$^{36}$
E.~Suchyta,$^{60}$
M.~E.~C.~Swanson,$^{29}$
G.~Tarle,$^{36}$
D.~Thomas,$^{3}$
C.~To,$^{45,25,26}$
T.~N.~Varga,$^{49,61}$
and A.~R.~Walker$^{18}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}
